\documentclass[letterpaper,11pt]{article}

\usepackage{array}
\usepackage[table]{xcolor}
\usepackage{xtab}
\usepackage{fancybox}
\usepackage{mdwlist}
\usepackage{amssymb}
\usepackage[colorlinks=true, urlcolor=blue]{hyperref}

% no page numbering
\pagestyle{empty}

\addtolength{\oddsidemargin}{-.875in}
\addtolength{\evensidemargin}{-.875in}
\addtolength{\textwidth}{1.75in}
\addtolength{\textheight}{1.75in}
\addtolength{\topmargin}{-1.0in}
\addtolength{\textheight}{2.0in}

% replace the circle bullets by little black squares
\renewcommand{\labelitemi}{\tiny $\blacksquare$}
% put some more space between row in tabular
\renewcommand{\arraystretch}{1.1}

\begin{document}

\begin{center}
  {\LARGE \bf Juan Miguel Pino}
\end{center}

\begin{tabular}{ll}
Web Page & \url{http://mi.eng.cam.ac.uk/~jmp84}, \url{https://github.com/jmp84} \\
Address & Facebook Ltd \\
        & 10 Brock Street \\
        & London NW1 3FG \\
Phone (cell) & TODO \\
E-mail & jmp84@cam.ac.uk \\
\end{tabular}


%\begin{itemize*}
%  \item {\bf Objective}: research position in machine translation / natural language processing.
%  \item {\bf Strengths}: strong background in machine translation and natural language processing, fluent in several languages.
%\end{itemize*}

\vspace{1cm}

\begin{xtabular}{p{0.2\textwidth} p{0.8\textwidth}}
  \multicolumn{2}{>{\columncolor[rgb]{0.73,0.78,0.85}[\tabcolsep][\tabcolsep]}c}{\Large \bf Work Experience} \\
   & \\
  {\bf 08/2015--present} & Research Scientist at Facebook. Currently working on machine translation system training and algorithm development. \\
  {\bf 08/2014--08/2015} & Research Scientist at Facebook London. \\
  {\bf 08/2013--12/2013} & Part-time research engineer at SDL/Language Weaver Cambridge. \\[3pt]
  {\bf 07/2011--09/2011} & Internship at Google. Worked on metrics and morphology. \\[3pt]
  {\bf 2010--2011}      & Supervisions for undergraduates in computer science at the University of Cambridge (courses: mathematical methods for computer science and computation theory). \\[3pt]
  {\bf 08/2007--08/2009} & Research Assistant at the Language Technologies Institute, Carnegie Mellon University. \\[3pt]
  {\bf 04/2007--08/2007} & Research internship at the Language Technologies Institute, Carnegie Mellon University. Built a French version of the REAP software, a tutoring system for vocabulary learning. \\[3pt]
  {\bf 09/2005--04/2006} & Tutoring undergraduate students in mathematics. \\[3pt]
  {\bf 2004--2005} & Leadership training in the French Navy: Junior Officer of the Watch, Assistant Officer for naval intelligence, aide-de-camp on board the Landing Ship Dock Ouragan from November 2004 to March 2005, part of the first year curriculum of the Ecole Polytechnique. \\[3pt]
  {\bf 08/2006} & Nurse's assistant in the trauma ward in a hospital in Novosibirsk, Russia. \\[3pt]
  {\bf 09/2000-07/2001} & Piano classes and piano accompaniment. \\[3pt]
\end{xtabular}

\vspace{0.4cm}

\begin{xtabular}{p{0.2\textwidth} p{0.8\textwidth}}
  \multicolumn{2}{>{\columncolor[rgb]{0.73,0.78,0.85}[\tabcolsep][\tabcolsep]}c}{\Large \bf Skills} \\
   & \\
  {\bf Languages} & Used daily: C++, Python, Java, Perl. Used sometimes: PHP/MySQL (maintained the REAP software written with PHP/MySQL), Matlab, R \\[3pt]
  {\bf NLP/Translation} & UCAM-SMT, Moses, MTTK Toolkit, SRILM Toolkit, KenLM Toolkit, Google OpenFst Libraries \\[3pt]
  {\bf Miscellaneous} & Maintain a 20-node Hadoop cluster, Linux scripting (Bash, Awk, etc.), Gnuplot, \LaTeX \\[3pt]
\end{xtabular}

\newpage

\begin{xtabular}{p{0.2\textwidth}p{0.8\textwidth}}
  \multicolumn{2}{>{\columncolor[rgb]{0.73,0.78,0.85}[\tabcolsep][\tabcolsep]}c}{\Large \bf Education} \\
   & \\
  {\bf 10/2009--12/2014} & Machine Intelligence Laboratory, Department of Engineering, University of Cambridge, PhD candidate. Advisor: Dr. William Byrne. \\
                        & Research focus: Hierarchical grammar extraction and estimation for machine translation, language generation applied to MT. \\
  {\bf 08/2009} & {\bf Awarded Master of Science in Language Technologies (GPA: 3.77)} \\[3pt]
  {\bf 08/2007--08/2009} & Language Technologies Institute, School of Computer Science, Carnegie Mellon University, M.S.'s candidate. Advisor: Dr. Maxine Eskenazi. \\
                  & Research: question generation. \\
                  & Courses: broad range of NLP courses, one linguistics course, two semesters of Chinese. \\[3pt]
  {\bf 08/2007} & {\bf Awarded Dipl\^{o}me d'Ing\'{e}nieur de l'Ecole Polytechnique (Master's level)} \\[3pt]
  {\bf 08/2004--04/2007} & Ecole Polytechnique, Paris. \\
                  & Major: computer science and math. \\[3pt]
  {\bf 09/2006} & {\bf Awarded BSc in Sciences} \\[3pt]
  {\bf 08/2004} & {\bf Admitted to the Ecole Polytechnique}, one of France's leading universities for science and engineering \\[3pt]
  {\bf 09/2001--07/2004} & Preparatory Classes for entrance examinations to the French Grandes Ecoles (track: math, physics, engineering science, computer science; Lyc\'ee Faidherbe, Lille). \\[3pt]
  {\bf 09/2000--07/2001} & Conservatories of Lille and Roubaix, awarded advanced diploma of piano with very high honors, gold medalist, final diploma of piano with high honors, second year in harmony magna cum laude, first year in piano accompaniment with high honors. \\[3pt]
  {\bf 07/2000} & Baccalaureate in sciences (track: math and physics) awarded with very high honors (Lyc\'ee F\'enelon, Lille). \\
\end{xtabular}

\vspace{0.4cm}

\begin{xtabular}{p{0.2\textwidth} p{0.8\textwidth}}
  \multicolumn{2}{>{\columncolor[rgb]{0.73,0.78,0.85}[\tabcolsep][\tabcolsep]}c}{\Large \bf Awards and Achievements} \\
   & \\
  {\bf 2013} & Cambridge University translation system {\bf ranks first} in Russian-English for BLEU at WMT13 (\url{http://matrix.statmt.org}). \\[3pt]
  {\bf 2012} & Cambridge University translation system {\bf ranks third} in the NIST12 evaluation task in Arabic-English. \\[3pt]
  {\bf 2011} & Reviewer for IJCNLP 2011 \\[3pt]
  {\bf 2010} & Cambridge University translation system {\bf ranks first} in French-English and {\bf second} in English-French for BLEU at WMT10 (\url{http://matrix.statmt.org}). \\[3pt]
  {\bf 10/2009--12/2012} & EPSRC DTA Studentship. \\[3pt]
  {\bf 10/2009--12/2011} & DARPA AGILE Studentship. \\[3pt]
  {\bf 2009--2011} & Serve on the Program Committee of the Workshop on Question Generation. \\[3pt]
  {\bf 09/2007--08/2009} & Carnegie Mellon University, Language Technologies Institute Research Assistant Fellowship. \\[3pt]
  {\bf 09/2007} & {\bf Prix d'Option} awarded by Ecole Polytechnique (ranked amongst three best internships in computer science; topic: build a French version of the REAP software, a tutoring system for vocabulary learning). \\[3pt]
%  {\bf 10/2007} & Contributed to the organization of the SLATE 2007 Workshop. \\[3pt]
\end{xtabular}

\begin{xtabular}{p{1.025\textwidth}}
  \multicolumn{1}{>{\columncolor[rgb]{0.73,0.78,0.85}[\tabcolsep][\tabcolsep]}c}{\Large \bf Publications} \\
   \begin{itemize*}
                   \item {\bf Pino, J.}, Waite, A., Xiao, T., de Gispert, A., Flego, F., Byrne, W. (2013) The University of Cambridge Russian-English System at WMT13. In {\it Proceedings of WMT13}.
                   \item {\bf Pino, J.}, Waite, A., Byrne, W. (2012) Simple and Efficient Model Filtering in Statistical Machine Translation. In {\it The Prague Bulletin of Mathematical Linguistics}.
                   \item {\bf Pino, J.} (2010) PhD First Year Report. {\it Machine Intelligence Laboratory, Department of Engineering, University of Cambridge.}
                   \item de Gispert, A., {\bf Pino, J.} and Byrne, W. (2010) Hierarchical Phrase-based Translation Grammars Extracted from Alignment Posterior Probabilities. In {\it Proceedings of the Conference on Empirical Methods in Natural Language Processing}.
                   \item {\bf Pino, J.}, Iglesias, G., de Gispert, A., Blackwood, G., Brunning, J. and Byrne, W. (2010) The CUED HiFST System for the WMT10 Translation Shared Task. In {\it Proceedings of the ACL Fifth Workshop on Statistical Machine Translation}.
                   \item Marujo, L., Lopes, J., Mamede, N., Trancoso, I., {\bf Pino, J.}, Eskenazi, M., Baptista, J. and Viana, C. (2009) Porting REAP to European Portuguese. In {\it Proceedings of the SLaTE Workshop on Speech and Language Technology in Education}. 
                   \item {\bf Pino, J.} and Eskenazi, M. (2009) Semi-Automatic Generation of Cloze Question Distractors Effect of Students' L1. In {\it Proceedings of the SLaTE Workshop on Speech and Language Technology in Education}. 
                   \item {\bf Pino, J.} and Eskenazi, M. (2009) An Application of Latent Semantic Analysis to Word Sense Discrimination for Words with Related and Unrelated Meanings. In {\it Proceedings of the 4th Workshop on Innovative Use of NLP for Building Educational Applications, NAACL/HLT}. 
                   \item {\bf Pino, J.} and Eskenazi, M. (2009) Measuring Hint Level in Open Cloze Questions. In {\it Proceedings of the 22nd FLAIRS Conference}. 
                   \item {\bf Pino, J.}, Heilman, M. and Eskenazi, M. (2008) A Selection Strategy to Improve Cloze Question Quality. In {\it Proceedings of the Workshop on Intelligent Tutoring Systems for Ill-Defined Domains, 9th International Conference on Intelligent Tutoring Systems}.  
                   \item Heilman, M., Zhao, L., {\bf Pino, J.}, and Eskenazi, M. (2008) Retrieval of Reading Materials for Vocabulary and Reading Practice. In {\it The 3rd Workshop on Innovative Use of NLP for Building Educational Applications, ACL}.
  \end{itemize*} \\
\end{xtabular}

\vspace{-0.1cm}

\begin{xtabular}{p{0.2\textwidth} p{0.8\textwidth}}
  \multicolumn{2}{>{\columncolor[rgb]{0.73,0.78,0.85}[\tabcolsep][\tabcolsep]}c}{\Large \bf Language Skills} \\
   & \\
  French  & Native language \\
  Spanish & Native language \\
  English & Fluent (TOEFL:117/120) \\
  German  & Very good (ZOP: 240.5) \\
  Russian & Very good oral, written working knowledge \\
  Chinese & Beginner ($\sim$ 300 characters) \\
\end{xtabular}

\vspace{0.4cm}

\begin{xtabular}{p{1.025\textwidth}}
  \multicolumn{1}{>{\columncolor[rgb]{0.73,0.78,0.85}[\tabcolsep][\tabcolsep]}c}{\Large \bf Miscellaneous} \\
   \\
  Driver's license, ocean navigation certificate \\
\end{xtabular}

\end{document}
